---
title: "Museum Data in MET"
subtitle: "A data analysis about collection diversities 1900 to 2020"
author: 
  - Rae Zhang
thanks: "Code and data are available at: https://github.com/JunweiZhang130/Museums_Data.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper aims to explore the change in collections of the Metropolitan Museum of Art (MET) over the years, focusing on the change of nationality, culture, and medium of the artwork collections. The research utilizes data made available by the MET, which includes information on more than 470,000 artworks in its collection. The paper discusses the change of collections over years, strengths and weaknesses of the dataset, and also highlights how the collections reveals biases and limitations in cultural studies."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

\newpage

# Introduction

Technology has all but taken over the modern world, and a big part of this digital revolution is data collection. Museums are no exception. As institutions preserve memories for our society, museums have tremendous amounts of data, which holds power and yields interesting ways to analyse artifacts, collections, objects and their creators in new ways.

This paper wants to explore the **change of collections in Metropolitan Museum of Art (MET)** over 150 years, and how the museum selects the highlights collection over years based on the artists, content, and the region of the artwork, and what kind of actions are taken as a result of this data. *We estimate that American artists would be the mainstream in the museum because of the museum's location, and the museums are accepting more artworks from artists from diverse background compare to the past.* By analyzing the dataset in the museum, we are able to determine the best way to serve the visitors and help museums better accomplish their own mission.

# Data

## Data Source and Methodology

The Metropolitan Museum of Art presents over 5,000 years of art from around the world for everyone to experience and enjoy. The Museum lives in two iconic sites in New York City---The Met Fifth Avenue and The Met Cloisters. Millions of people also take part in The Met experience online.

Since it was founded in 1870, The Met has always aspired to be more than a treasury of rare and beautiful objects. Every day, art comes alive in the Museum's galleries and through its exhibitions and events, revealing both new ideas and unexpected connections across time and across cultures[@ypsilantis2021the].

The MET provides select datasets of information on more than 477,804 artworks in its Collection for unrestricted commercial and noncommercial use. To the extent possible under law, The Metropolitan Museum of Art has waived all copyright and related or neighbouring rights to this dataset using Creative Commons Zero. This work is published from: The United States Of America. The data is in CSV format.

The Museum dedicates select artworks in its collectionm, both works it believes to be in the public domain and those under copyright or other restrictions―to the public domain.People can download, share, modify, and distribute the data for any purpose, including commercial and noncommercial use, free of charge and without requiring permission from the Museum.

## Data Collection

The Metropolitan Museum of Art collected the data for their dataset from their internal collection management system, called the Museum System (TMS). TMS is a database that tracks information about each object in the museum's collection, including its title, artist, date, medium, dimensions, provenance, and exhibition history.

The MET's staff members enter and update this information in TMS as they catalog new acquisitions or revise existing records over years. The information in TMS is then used to create the museum's online collection database, which includes images and descriptions of each object.[@citeMET]

## Data Cleaning

To begin the data cleaning process, we first reviewed the dataset and used a set of questions to guide our variable selection. Our research goal is to analyze the collection gathering in the MET, and to answer several key questions about the museum's artwork, including:

-   The department with the largest number of artworks

-   The cultures that are most represented in the collection

-   The types of artists from different nationalities' artwork that are most prominent in the overall collection

-   The representation of highlighted artifacts across all collections

-   The trends in accession over time and potential factors that may impact accession

Based on these research questions, we identified several variables that we believed could help answer these questions, including **Object ID, Highlight, Timeline_Work, Department, AccessionYear, Object Name, Title, Culture, Artist Display Name**, and **Artist Nationality**.

After identifying these variables, we then proceeded to drop all missing values from the dataset that showed N/A. We also standardized the formatting of the **Country** and **Culture** variable, as the recording of this variable was done by different people and in different formats over the years. By cleaning and standardizing the data, we aimed to ensure that our subsequent data analyses would be more accurate and effective in answering our research questions.

## Data Analysis

We obtained the dataset from the MET museum Github [@citeMET]. Data can be downloaded from Met Github directly. We loaded in, cleaned and analyzed the data using `R` [@citeR], `dplyr` [@citedplyr], `tidyverse` [@citetidyverse], `haven` [@citehaven], `kableExtra` [@citekableExtra], `readr` [@citereadr], `ggplot2` [@citeggplot2], `stringr` [@citestringr], and `forcats` [@citeforcats] packages.

# Results

```{r}
#| echo: false
#| warning: false
#| message: false

# Loading in datasets and library
library(dplyr)
library(knitr)
library(kableExtra)
library(readr)
library(ggplot2)
library(stringr)
library(forcats)


# assuming your dataset is called cleaned_data and is stored in the "outputs" folder
cleaned_data <- read_csv(here::here("outputs/cleaned_data.csv"))

```

## Amount of Artworks in Various Departments 

The Metropolitan Museum of Art (MET) has 19 departments dedicated to different collections of art objects from various cultures and time periods. Each department has a unique focus, ranging from Drawings and Prints to Islamic Art to Libraries.

We examined the total artwork amount in each department. We found that the Drawing and Painting department had the most number of objects with just over 16,7152, while the Libraries department had the smallest collection of 390 objects.

We observed that there was a significant variation in the distribution of objects across departments. For instance, the European Sculpture and Decorative Arts department had a collection of 42,934 objects, which was significantly larger than the number of objects in the Arts of Africa, Oceania, and the Americast, which had a collection of only 12,335 objects. The variation in collection size could be attributed to factors such as the popularity of different art forms, the historical significance of certain periods or cultures, and the availability of art objects for acquisition.

Our findings provide valuable insights into the distribution of artwork at the MET, shedding light on the representation of different art forms and cultures in the museum's holdings.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-1
#| tbl-cap: MET Collections by Department

# count the number of rows in each department
department_counts <- cleaned_data %>% 
  group_by(Department) %>% 
  summarize("Number of Collections" = n()) %>% 
  rename(Department = Department) %>%
  arrange(desc(`Number of Collections`))

# create a formatted table
kable(department_counts) %>%
  kable_styling(latex_options = "HOLD_position", 
                font_size = 10)

```

```{r}
#| label: fig-nationalities
#| fig-cap: Top 10 Artist Nationalities by Artwork Collections
#| echo: false
#| warning: false
#| message: false

# filter out rows with missing or NA values in Nationality column
cleaned_data$`Artist Nationality` <- gsub("\\|", "", cleaned_data$`Artist Nationality`)

artworks_by_nationality <- cleaned_data %>%
  mutate(artist_nationality = case_when(
    grepl("(?i)american", `Artist Nationality`) ~ "American",
    grepl("(?i)british", `Artist Nationality`) ~ "British",
    grepl("(?i)french", `Artist Nationality`) ~ "French",
    grepl("(?i)italian", `Artist Nationality`) ~ "Italian",
    grepl("(?i)spanish", `Artist Nationality`) ~ "Spanish",
    grepl("(?i)german", `Artist Nationality`) ~ "German",
    grepl("(?i)chinese", `Artist Nationality`) ~ "Chinese",
    grepl("(?i)japanese", `Artist Nationality`) ~ "Japanese",
    grepl("(?i)russian", `Artist Nationality`) ~ "Russian",
    TRUE ~ `Artist Nationality`
  )) %>%
  group_by(artist_nationality) %>%
  summarize(num_artworks = n()) %>%
  arrange(desc(num_artworks)) %>%
  filter(!is.na(artist_nationality) & artist_nationality != "" & str_detect(artist_nationality,"[[:alnum:]]+")) %>%
  head(10)

# adjust order of bars
artworks_by_nationality$artist_nationality <- forcats::fct_relevel(artworks_by_nationality$artist_nationality, "Austrian", after = Inf)

# plot bar chart
ggplot(artworks_by_nationality, aes(x = artist_nationality, y = num_artworks)) +
  geom_bar(stat = "identity", 
           fill = "blue", 
           alpha = 0.6) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "Artist Nationality", y = "Number of Collections", title = "Top 10 Artist Nationalities by Artwork Collections") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, 
                                  face = "bold", 
                                  hjust = 0.5),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1, 
                                   size = 12, 
                                   family = "sans"),
        axis.text.y = element_text(size = 12, 
                                   family = "sans"),
        axis.title = element_text(size = 12, 
                                  family = "sans"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```

## Artist Nationalities

In our analysis of the Metropolitan Museum of Art's (MET) dataset, we explored the representation of different artist nationalities in the museum's collections. Using the "Artist Nationality" variable, we identified the top 10 nationalities represented among the artists in the dataset([@fig-nationalities]).

The top 10 artist nationalities in the MET's collections, ranked by the total number of artwork objects, are as follows: American - 47,797; French - 42,748; Italian - 29,910; British - 22,491; German - 18,293; Japanese - 15,097; Spanish - 12,599; Chinese - 10,322; Dutch - 9,876; Flemish - 7,303

Our analysis also revealed that the majority of the artwork in the MET's collections were created by artists from the United States, with over 60,000 objects. This was followed by French artists with over 42,000 objects, and Italian artists with over 29,000 objects.

```{r}
#| label: fig-nationalitieshighlights
#| fig-cap: Top 10 Artist Nationalities by Highlight Artwork Collections
#| echo: false
#| warning: false
#| message: false

cleaned_data$`Artist Nationality` <- gsub("\\|", "", cleaned_data$`Artist Nationality`)

artworks_by_nationality_highlight <- cleaned_data %>%
  mutate(artist_nationality = case_when(
    grepl("(?i)american", `Artist Nationality`) ~ "American",
    grepl("(?i)british", `Artist Nationality`) ~ "British",
    grepl("(?i)french", `Artist Nationality`) ~ "French",
    grepl("(?i)italian", `Artist Nationality`) ~ "Italian",
    grepl("(?i)spanish", `Artist Nationality`) ~ "Spanish",
    grepl("(?i)german", `Artist Nationality`) ~ "German",
    grepl("(?i)chinese", `Artist Nationality`) ~ "Chinese",
    grepl("(?i)japanese", `Artist Nationality`) ~ "Japanese",
    grepl("(?i)russian", `Artist Nationality`) ~ "Russian",
    TRUE ~ `Artist Nationality`
  )) %>%
  filter(Highlight == "TRUE") %>%
  group_by(artist_nationality) %>%
  summarize(num_artworks = n()) %>%
  arrange(desc(num_artworks)) %>%
    filter(!is.na(artist_nationality) & artist_nationality != "" & str_detect(artist_nationality,"[[:alnum:]]+")) %>%
  head(10)

ggplot(artworks_by_nationality_highlight, aes(x = artist_nationality, y = num_artworks)) +
  geom_bar(stat = "identity", 
           fill = "blue", 
           alpha = 0.6) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "Artist Nationality", 
       y = "Number of Highlight Collections", 
       title = "Top 10 Artist Nationalities by Artwork Collections") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, 
                                  face = "bold", 
                                  hjust = 0.5),
        axis.text.x = element_text(angle = 45, 
                                   hjust = 1, 
                                   size = 12, 
                                   family = "sans"),
        axis.text.y = element_text(size = 12, 
                                   family = "sans"),
        axis.title = element_text(size = 12, 
                                  family = "sans"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        )
```

## Artist Nationalities and Highlight Artworks

In [@fig-nationalitieshighlights], we examined the top 10 artist nationalities whose artwork was highlighted in the MET museum. We defined highlighted artwork as objects that were labelled with a "Highlight" tag in the dataset. Our analysis showed that American artists had the highest number of highlighted artwork with 387 objects, followed by French artists with 244 objects, and Italian artists with 116 objects. The other nationalities in the top 10 were German, British, Dutch, Netherlandish, Japanese, Spanish, Chinese.

Furthermore, we analyzed that even spanish artworks are not one of the top 10 large collections in the dataset, they become one of the 10 nationalities owns most highlights artworks.

```{r}
#| label: fig-collectionobjects
#| fig-cap: Top 10 Objects Mediums in Artwork Collections
#| echo: false
#| warning: false
#| message: false
#| results: "asis"

# Create a data frame for the bar chart
object_counts_bar <- cleaned_data %>%
  filter(`Object Name` != "Other") %>%
  group_by(`Object Name`) %>%
  summarize(count = n()) %>%
  top_n(10, wt = count) %>%
  mutate(`Object Name` = fct_reorder(`Object Name`, count))

# Create the bar chart
ggplot(object_counts_bar, aes(x = `Object Name`, y = count, fill = `Object Name`)) +
  geom_col() +
  labs(title = "Top 10 Object Medium in Collections", 
       x = "Medium", 
       y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        plot.title = element_text(hjust = 0.5)) +
  theme(legend.position = "none")


```
## Artworks and Mediums

[@fig-collectionobjects] showed that the most popular object medium in the MET's collection was prints. This was followed by photograph and drawings. Other popular mediums included book, fragment, and piece. Meanwhile, we can see Print has the largest collections among all other object mediums.

```{r}
#| label: fig-accession
#| fig-cap: Number of Artworks Accessioned Over Year
#| echo: false
#| warning: false
#| message: false
#| results: "asis"

accession_data <- cleaned_data %>%
  mutate(AccessionYear = as.Date(paste0(AccessionYear, "-01-01"))) %>%
  group_by(AccessionYear) %>%
  summarize(num_artworks = n())

ggplot(accession_data, aes(x = AccessionYear, y = num_artworks)) +
  geom_line() +
  labs(title = "Number of Artworks Accessioned Over Year", 
       x = "Year", 
       y = "Count") +
  theme(plot.title = element_text(hjust = 0.5))


```

## Artworks Accession Over Years

The accession year of artwork in the Metropolitan Museum of Art (MET) provides valuable insights into the museum's acquisition history and patterns of collecting. We analyzed the number of artwork accessions over the years to understand the trends in the museum's collection over time in [@fig-accession]. Our analysis revealed that the number of accessions per year has varied significantly over the course of the museum's history. For instance, the year with the highest number of accessions was 1960s. In contrast, the year with the lowest number of accessions was 2020. Furthermore, we examined the distribution of artwork accessions by decade. We found that the number of artwork access reached a peak in every 50 years. The 2010s had the second highest number of accessions, followed by the 1920s.

```{r}
#| label: fig-accessionhighlight
#| fig-cap: Number of Highlight Artworks Accessioned Over Year
#| echo: false
#| warning: false
#| message: false
#| results: "asis"

highlighted_artwork <- cleaned_data %>% 
  filter(Highlight == "TRUE") %>% 
  group_by(AccessionYear) %>% 
  summarize(count = n())

ggplot(highlighted_artwork, aes(x = AccessionYear, y = count)) +
  geom_line() +
  labs(title = "Number of Highlighted Artworks", 
       x = "Year", 
       y = "Count") +
  ylim(0, 120)+
  theme(plot.title = element_text(hjust = 0.5))

```

## Highlight Artworks Accession Over Years

The Met defined "highlight artwork" as those that have been prominently featured in the museum's exhibitions or publications. [@fig-accessionhighlight] revealed that the number of highlight artwork accessions varied from year to year. Since 1900, every year the MET has acquired a new highlight artworks. We also looked at the total number of artwork accessions per year and found that there was a general trend of increasing accessions over time. In the early 1900s and before, the number of accessions was relatively low, with fewer than 500 accessions per year. However, in the latter half of the 20th century, the number of accessions increased significantly.

# Discussion

## Bias and Histories about MET Collections

```{r}
#| label: fig-countries
#| fig-cap: Artworks Nationalities Accessed from 1900 to 2020
#| echo: false
#| warning: false
#| message: false
#| results: "asis"

# filter for American, French, and Italian artists only
artist_nationalities <- c("American", "French", "Italian")
filtered_data <- cleaned_data %>%
  filter(`Artist Nationality` %in% artist_nationalities)

# calculate counts of artworks per nationality and year
counts_data <- filtered_data %>%
  group_by(`Artist Nationality`, `AccessionYear`) %>%
  summarize(count = n())

# calculate the mode of artwork counts per nationality per year
mode_data <- counts_data %>%
  distinct(`Artist Nationality`, `AccessionYear`, .keep_all = TRUE) %>%
  group_by(`Artist Nationality`, `AccessionYear`) %>%
  summarize(mode_count = as.numeric(names(sort(table(count), decreasing = TRUE))[1]))

# plot the histogram of artwork counts per nationality per year
ggplot(counts_data, aes(x = AccessionYear)) +
  geom_histogram(bins = 15) +
  labs(title = "Artworks Nationalities Accessed from 1900 to 2020", 
       x = "Year", 
       y = "Count") +
theme_minimal() +
  facet_wrap(vars(`Artist Nationality`), 
             scales = "free_y", 
             ncol = 1) +
  scale_x_log10() +
  labs(fill = NULL) +
  # add the mode values as a line plot
  geom_line(data = mode_data,
            aes(x = `AccessionYear`,
                y = mode_count,
                color = `Artist Nationality`))

```

From [@fig-countries], we can see there is obvious peaks of amount of artwork accessions over the years in artworks from all three nations. The increase in the number of artwork accessions at the Metropolitan Museum of Art from 1900 to 2020 is likely due to several factors, including the growth of the museum's collection, increased public interest in art and culture, and the museum's expanded efforts to acquire works from diverse cultures and time periods. From [@fig-nationalities], we can tell that MET had a larger number of artworks accessioned from American artists compared to French artists and Italian artists. This could indicate that even though the mission of MET is "The Metropolitan Museum of Art collects, studies, conserves, and presents significant works of art across time and cultures in order to connect all people to creativity, knowledge, ideas, and one another", they still show significant preference for American art or a stronger focus on collecting American art. 

Another interesting finding is that while American artists had the largest number of artworks accessioned overall, French artists had the highest average number of artworks accessioned per artist. This shows the history ties MET has with France - When the MET was founded in 1870, France was a dominant force in the art world. As a result, the museum began collecting French artworks early on, and this trend continued over the years. After MET earns a reputation about its French artwork collection, it has also actively acquired French artworks through purchases and auctions over the years. The museum has a large acquisition budget towards European artworks, which has enabled it to acquire many important French artworks and artworks frmo other European nations. 

```{r}
#| label: fig-2nations
#| fig-cap: Artworks accession by decade and artist from America and French
#| echo: false
#| warning: false
#| message: false
#| results: "asis"

# filter for American, French, China, and Japan nationalities
artist_nationalities <- c("American", "French")
filtered_data <- cleaned_data %>%
  filter(`Artist Nationality` %in% artist_nationalities,
         AccessionYear >= 1920 & AccessionYear <= 2020,
         Department %in% c("Print", "Photographs", "Drawing"))

# group by AccessionY ear, Department, and Artist Nationality and calculate the count of artworks
grouped_data <- filtered_data %>%
  group_by(AccessionYear, Department, `Artist Nationality`) %>%
  summarize(count = n())

# mutate Accession Year as a factor variable and group by decades
grouped_data <- grouped_data %>%
  mutate(AccessionYear = factor(10 * (as.numeric(AccessionYear) %/% 10)))

# create boxplot
ggplot(grouped_data, aes(x = AccessionYear, y = count)) +
  geom_boxplot(alpha = 0.8, show.legend = FALSE) +
  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
  facet_wrap(vars(`Artist Nationality`), ncol = 1) +
  scale_y_log10() +
  labs(x = NULL)

```

## Need to Represent Art in Diversities

[@fig-2nations] shows the number of artworks acquired by the Metropolitan Museum of Art (MET) from 1900 to 2020, grouped by decade and artists from American and France. From the graph, we can see that the MET has acquired a significant number of artworks from both American and French artists, with the number of American artworks being consistently higher than French artworks throughout the 20th century. We can also find that the amount of American artworks has steadily increased while French artwork collections are decreasing, which shows the museum is more and more dominated by local arts, which drives it off the museum's mission. 

The graph also shows that the number of artworks acquired by the MET has varied over time, with some decades seeing a significant increase or decrease in the number of acquisitions. For example, there was a significant increase in the number of artworks acquired by the MET in the 1950s to 1970s, possibly due to the post-World War II economic boom.

## Misrepresenting the World Culture

Through the graphs and tables, I find that MET's collections are heavily dominated by American arts, which does not match the MET's museum's vision and mission, which is collect the highlight arts from cultures all over the world. The misrepresentation of cultures can lead to a biased view of a culture, especially when major highlight artworks are only from America and Europe, the museum will represent a narrow range of themes, styles, or time periods within the world culture. For example, if an art museum only highlights American art in its gallery, it may present a skewed and incomplete view of the complex and diverse culture, and lead visitor to neglect other cultures which should be paying attention to preserve, too. Similarly, accession year data can perpetuate stereotypes or misconceptions about a culture if the selected artworks only reflect a limited period of its history or a particular moment of cultural exchange.

Therefore, it is important for art museums to consider the context and significance of each artwork when selecting pieces for metadata highlight and accession year data. By choosing a diverse range of artworks that represent different themes, styles, and time periods, museums can provide a more accurate and nuanced representation of a culture. Additionally, museums should make an effort to include works by lesser-known or underrepresented artists, as well as artworks that challenge or subvert dominant narratives about a culture. This can help to promote a more inclusive and equitable representation of cultures in art museums.

# Conclusion

## Strength and Weaknesses

The Metropolitan Museum of Art's open dataset is a valuable resource for data scientists and researchers looking to study art, history, and culture. However, like any dataset, it has its strengths and weaknesses.

The dataset from the MET offers several strengths that make it a valuable resource for analysis. First, the dataset is large and diverse, containing over 470,000 records of art objects from around the world and across time periods. This diversity provides a vast collection for analysis, allowing researchers to explore various topics from different angles. Another strength is that the dataset is available to anyone for free, making it easily accessible to researchers and art enthusiasts alike. This open access encourages more people to use and explore the dataset, promoting broader participation and facilitating collaborative research. In addition, the dataset contains rich metadata about each object, such as its title, artist, date, medium, and dimensions. This information provides a wealth of data for analysis, offering researchers insights into the cultural and historical contexts of the objects and the artists who created them.

However, this data still has some limitations that must be considered. One limitation is that the data is collected and uploaded in different formats over time, which can make it challenging to compare and analyze data across different periods. Another limitation is that the dataset primarily includes text-based information, such as titles and descriptions, and images of the art objects. Other types of data, such as audio or video recordings, are not included, which may limit the analysis of this research. Moreover, missing data is a large issue in the dataset, as some objects are lack detailed descriptions or are missing important metadata, for example, genders are misrepresented in "|" and "||", which makes it impossible to figure out the meanings. This limitation can limit the reliability and validity of analyses, and it is important to consider the completeness and accuracy of the data when conducting research using this dataset.

## Next Step

To address the misrepresentation of cultures in art museums, it is important for museums to choose a diverse range of artworks that represent different cultures, mediums, and time periods. This can provide a more accurate and nuanced representation of the world culture and promote a more inclusive and equitable representation of cultures in art museums. 

In addition, it is important to consider the limitations of the dataset, such as the collection and uploading of data in different formats over time, the exclusion of other types of data, and missing data. The museum should establish clear policies and handbook about data collecting and updating, so the data can still be useful and carry its meaning over years. By acknowledging these limitations and selecting a diverse range of artworks, museums can promote a more accurate and comprehensive representation of world cultures for visitors.


\newpage

# References
